Paper figures

### 2020-09-24 notebooks/paper_plots_0909.Rmd
Changed AUC y axis label amd converted to bar plot

auc_plot <- auc_data%>%
    ggplot(aes(x=variable_0,y=r))+
    geom_point(aes(color=variable_0))+#, position=position_jitterdodge())+
    geom_line(aes(group=group),color='grey')+
    facet_grid(rows = vars(group), labeller = labeller(group=facet_labels))+
    theme_bw()+
    ylab("AUC")+
    xlab("Deletion parameter")+
    labs(color = "Deletion\nparameter")+
    scale_x_discrete(labels = c(
                                "Degree",
                                "Betweenness",
                                "Effectiveness",
                                "Closeness",
                                "Eigencentrality",
                                "Random",
                                "Sensitivity"))+
    scale_colour_brewer(palette = "Set1", labels= c(
                                "Degree",
                                "Betweenness",
                                "Effectiveness",
                                "Closeness",
                                "Eigencentrality",
                                "Random",
                                "Sensitivity"))+
   theme(legend.position='right')

@@

deletion_lgn <- cowplot::get_legend(auc_plot)
plot_grid(deletion_plot+    theme(legend.position='')
, auc_plot+    theme(legend.position='')
,deletion_lgn, nrow=1, rel_widths =c(0.45, 0.45,.1), labels=c('A','B'))
ggsave('reports/figures/paper_figures_0916/fig3.png',width=12)

@@

#p3 = 
sensor_connectivity_plot <- 
    ggplot()+
    geom_boxplot(data=sensor_connectivity_df%>%filter(type=='random'),
                 aes(x=data,y=ratio,color=type))+
#    geom_jitter()+
    geom_point(data=sensor_connectivity_df%>%filter(type=='real'),
            aes(x=data,y=ratio,color=type, group=data))+
               #position=position_jitter(), aes(shape=data))+
    scale_color_discrete(labels=c('Random sampled set', 'Sensors'))+
    scale_x_discrete(labels=network_labels)+
  guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
    xlab('Network type')+ylab('Ratio of between group edges\nto outgroup edges')+
    theme_bw()
neighbor_degree_plot <- combined_df%>%
    ggplot(aes(x=neighbor_degree,y=sens_norm))+
    facet_grid(rows=vars(data),labeller = labeller(data=facet_labels))+
    geom_point()+
    theme_bw()+
    xlab('Average neighbor degree')+
    ylab('Sensitivity')
plot_grid(neighbor_degree_plot, sensor_connectivity_plot, nrow=2 , labels=c('A','B'))
ggsave('reports/figures/paper_figures_0916/fig4.png')

@@

>>>>

auc_plot <- auc_data%>%
    ggplot(aes(x=variable_0,y=r))+
    geom_bar(aes(fill=variable_0),stat='identity')+
 #   geom_point(aes(color=variable_0))+#, position=position_jitterdodge())+
#    geom_line(aes(group=group),color='grey')+
    facet_grid(rows = vars(group), labeller = labeller(group=facet_labels))+
    theme_bw()+
    ylab("Cost of fractioning the network (AUC)")+
    xlab("Deletion parameter")+
    labs(fill = "Deletion\nparameter")+
    scale_x_discrete(labels = c(
                                "Degree",
                                "Betweenness",
                                "Effectiveness",
                                "Closeness",
                                "Eigencentrality",
                                "Random",
                                "Sensitivity"))+
    scale_fill_brewer(palette = "Set1", labels= c(
                                "Degree",
                                "Betweenness",
                                "Effectiveness",
                                "Closeness",
                                "Eigencentrality",
                                "Random",
                                "Sensitivity"))+
   theme(legend.position='right')

@@

deletion_lgn <- cowplot::get_legend(auc_plot)
plot_grid(deletion_plot+    theme(legend.position='')
, auc_plot+    theme(legend.position='')
,deletion_lgn, nrow=1, rel_widths =c(0.4, 0.5,.1), labels=c('A','B'))
ggsave('reports/figures/paper_figures_0916/fig3.png',width=12)

@@

#p3 = 
sensor_connectivity_plot <- 
    ggplot()+
    geom_boxplot(data=sensor_connectivity_df%>%filter(type=='random'),
                 aes(x=data,y=ratio,color=type))+
#    geom_jitter()+
    geom_point(data=sensor_connectivity_df%>%filter(type=='real'),
            aes(x=data,y=ratio,color=type, group=data))+
               #position=position_jitter(), aes(shape=data))+
    scale_color_discrete(labels=c('Random sampled set', 'Sensors'))+
    scale_x_discrete(labels=network_labels)+
  guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
    xlab('Network type')+ylab('Ratio of between group edges\nto outgroup edges')+
    theme_bw()
neighbor_degree_plot <- combined_df%>%
    ggplot(aes(x=sens_norm,y=neighbor_degree))+
    facet_grid(cols=vars(data),labeller = labeller(data=facet_labels))+
    geom_point()+
    theme_bw()+
    ylab('Average neighbor degree')+
    xlab('Sensitivity')
plot_grid(neighbor_degree_plot, sensor_connectivity_plot, nrow=2 , labels=c('A','B'))
ggsave('reports/figures/paper_figures_0916/fig4.png')

@@

```{r}
convert_networkx_to_igraph <- 			# 
    function
(
 	nx_object,
    df
)
{
    nx =  reticulate::import("networkx")
    ig = igraph::graph.adjacency(nx$adjacency_matrix(nx_object), mode = 'undirected')
    ig = igraph::set_vertex_attr(ig , name =  'orf_name', value  = (df$orf_name))
    igraph::set_vertex_attr(ig, "pos", nxqjjj
    ig

}
```
```{r}
plot_network_spring <- 			# 
    function
(
    gc , df , pos , ... 	
)
{
 pcc_gc_ig = convert_networkx_to_igraph(gc, df)

png('tmp.png')
plot(pcc_gc_ig, vertex.size=1, vertex.label=NA, layout = pos)
dev.off()

}
pcc_gc = py$pcc_gc
pcc_gc_pos = matrix(unlist(py$pcc_gc_pos),ncol=2,byrow=TRUE)
plot_network_spring(pcc_gc, pcc_df, pcc_gc_pos)
```
